### 2020-03-04 README.Rmd
Made some changes but not running! SOrry. I left a note where the problem is.
comment out the parts that don't work

```{r}
bw_focal_vs_comp <- create_focal_vs_comp(bw_growth_df, max_dist, cv_fold_size, bw_specs)
scbi_focal_vs_comp <- create_focal_vs_comp(scbi_growth_df, max_dist, cv_fold_size, scbi_specs)

>>>>

**DA NOTE: THIS IS BROKEN HERE!! The problem is the new `sf` structure of `growth_df` breaks `get_cv_fold_info` which is called in `create_focal_vs_comp`. Also at some point `fold` in `growth_bf` became `foldID`. So I had to go change that in a bunch of the package code.**

```{r}
#bw_focal_vs_comp <- create_focal_vs_comp(bw_growth_df, max_dist, cv_fold_size, bw_specs)
#scbi_focal_vs_comp <- create_focal_vs_comp(scbi_growth_df, max_dist, cv_fold_size, scbi_specs)
